Summer 2024 Report

### 2025-01-31 Relations/Report.tex
Report update on implications and CEs

\begin{table}[h!]
  \centering
  \caption{Global implications}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
  \hline
  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & \red{CR} , SN \\
  \hline
  \textbf{WNFP} & {CE-11}, {CE-9}  & CR, {CE-6}  & CE-11 , {CE-9} & CR, ?   & \red{CR} , SN \\
  \hline
  \textbf{UN} & {CE-3}, {CE-12}  & CR, {CE-6}  & CE-3, {CE-9}  & CR, {CE-3}  & \red{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Global implications - WCR}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
  \hline
  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & CR , SN \\
  \hline
  \textbf{WNFP} & ?, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & CR , SN \\
  \hline
  \textbf{UN} & ?, {CE-9}  & CR, {CE-6}  & \red{CR}, {CE-9}  & CR, ?  & CR , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

@@

>>>>

\begin{table}[h!]
  \centering
  \caption{Global implications}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
  \hline
  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & \red{CR} , {CE-9} & CR, ?   & \red{CR} , SN \\
  \hline
  \textbf{WNFP} & {CE-11}, {CE-9}  & CR, {CE-6}  & CE-11 , {CE-9} & CR, ?   & \red{CR} , SN \\
  \hline
  \textbf{UN} & {CE-3}, {CE-12} and CE-9  & CR, {CE-6}  & CE-3, {CE-9}  & CR, ?  & \red{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Global implications - WCR}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, {CE-9}  & CR, {CE-6}  & CR , {CE-9}  & CR, ?  & CR , SN \\
  \hline
  \textbf{RP} & CR, {CE-9}  & CR, {CE-6}  & {CR} , {CE-9} & CR, ?   & CR , SN \\
  \hline
  \textbf{WNFP} & CE-1.2, {CE-9}  & CR, {CE-6}  & {CR} , {CE-9} & CR, ?   & CR , SN \\
  \hline
  \textbf{UN} & CE-1.1, {CE-9}  & CR, {CE-6}  & {CR}, {CE-9}  & CR, ?  & CR , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

@@

\subsection*{Counterexample 1.1}
\begin{center}

      % Arrows
      \draw[->] (b) to [bend left] (c);
      \draw[->] (c) to [bend left] (b);
      \draw[->] (b) -- (a);
      \draw[->] (c) -- (d);
      \draw[->, loop] (d) to (d);

  \end{tikzcd}

\end{center}
Counterexample to:
\begin{itemize}
  \item (Global) WCR, UN, and WR $\implies$ WNFP
\end{itemize}

\subsection*{Counterexample 1.2}
\begin{center}

      % Arrows
      \draw[->] (b) to [bend left] (c);
      \draw[->] (c) to [bend left] (b);
      \draw[->] (b) -- (a);
      \draw[->] (c) -- (d);
      \draw[->, loop] (d) to (d);
      \draw[->, loop] (a) to (a);

  \end{tikzcd}

\end{center}
Counterexample to:
\begin{itemize}
  \item (Global) WCR, WNFP, and WR $\implies$ RP
\end{itemize}
